### 2015-07-04 analysis/figures/paper_figures.tex
Add old changes

\subsection{Steady-State Visual Evoked Potential}
During the SSVEP experiment, and LED was flashed at 40 Hz with a 50\% duty cycle.
For both a resting state and experimental period, Welsh's method was used to compute the power spectral density with a window length of 2 seconds and an overlap of 25\%.
The ratio of the experimental power with the resting state power at each frequency is shown.
All data within 3 Hz of a 60 Hz harmonics are excluded due to showing heavy artifacts from electrical equipment.
The background data includes data more than 3 Hz away from harmonics of 40 Hz, and the harmonic data takes the maximum power at a frequency within 3 Hz of each harmonic.
All experimental measurements lasted between 22.5 seconds and 57.0 seconds, and all resting state measurements lasted between 28.8 seconds and 60.7 seconds.
\subsection{Steady-State Auditory Evoked Potential}
[Same processing as SSVEP]
All experimental measurements lasted between 29.0 seconds and 59.2 seconds, and all resting state measurements lasted between 4.4 seconds and 59.0 seconds.
[Subject 2 has very short resting state measurements for SSAEP - shortest for subject 1 is 28.4 seconds]
\subsection{Cardiac Artifacts and Removal}
The cardiac data is high-passed.
The maximum in a 0.18 second interval is considered the R peak.
The segments are split 0.63 between the R peaks (this is so that the P-wave and T-wave end up on opposite sides).
The mean is computed for each time step relative to the R peak, and a zero is averaged in for trials that do not extend that far out (the R peaks are not exactly equally centered).
In some sense, this indicates uncertainty in what the cardiac artifacts are at that time, so a smaller adjustment is made.
The mean for the cardiac shape is then subtraced out from each electrode.
\label{section:cardiac}
\begin{figure}[H]
\begin{center}
\includegraphics[scale=1.0]{surgical_methods.pdf}
\caption{Surgical approach, anatomy imaging.}
\label{fig:surgical}
% Figure 1
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
\includegraphics[scale=0.5]{impedance.pdf}
\end{tabular}
\caption{Impedance characterization.}
\label{fig:impedance}
% Figure 4
\end{center}
\end{figure}

>>>>

\subsection{Steady-State Visual Evoked Potential}
During the SSVEP experiment, and LED was flashed at 40 Hz with a 50\% duty cycle.
For both a resting state and experimental period, Welsh's method was used to compute the power spectral density with a window length of 2 seconds and an overlap of 25\%.
The ratio of the experimental power with the resting state power at each frequency is shown.
All data within 3 Hz of a 60 Hz harmonics are excluded due to showing heavy artifacts from electrical equipment.
The background data includes data more than 3 Hz away from harmonics of 40 Hz, and the harmonic data takes the maximum power at a frequency within 3 Hz of each harmonic.
All experimental measurements lasted between 22.5 seconds and 57.0 seconds, and all resting state measurements lasted between 28.8 seconds and 60.7 seconds.
\subsection{Steady-State Auditory Evoked Potential}
[Same processing as SSVEP]
All experimental measurements lasted between 29.0 seconds and 59.2 seconds, and all resting state measurements lasted between 4.4 seconds and 59.0 seconds.
[Subject 2 has very short resting state measurements for SSAEP - shortest for subject 1 is 28.4 seconds]
\subsection{Cardiac Artifacts and Removal}
The cardiac data is high-passed.
The maximum in a 0.18 second interval is considered the R peak.
The segments are split 0.63 between the R peaks (this is so that the P-wave and T-wave end up on opposite sides).
The mean is computed for each time step relative to the R peak, and a zero is averaged in for trials that do not extend that far out (the R peaks are not exactly equally centered).
In some sense, this indicates uncertainty in what the cardiac artifacts are at that time, so a smaller adjustment is made.
The mean for the cardiac shape is then subtraced out from each electrode.
\label{section:cardiac}
\begin{figure}[H]
\begin{center}
\includegraphics[scale=1.0]{../../../../Dropbox/Bryan_Easter/paper_figures/anatomy v1.pdf}
\caption{Surgical approach, anatomy imaging.}
\label{fig:surgical}
% Figure 1
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
\raisebox{-0.5\height}{\includegraphics[scale=0.4]{../../../../Dropbox/Bryan_Easter/paper_figures/impedance_characterization-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.4]{../../../../Dropbox/ExtractImpedancesFromDTAGAMRYFiles/impedance-crop.pdf}} \\
\vspace{0.5cm} \\
\raisebox{-0.5\height}{\includegraphics[scale=0.4]{../../../../Dropbox/Bryan_Easter/paper_figures/system_characterization-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.4]{../../../../Dropbox/analyzesinewaves/system-crop.pdf}}
\end{tabular}
\caption{Impedance characterization.}
\label{fig:impedance}
% Figure 4
\end{center}
\end{figure}
